Quality measure notes

### 2021-08-30 StateOfPractice/Ao-Report/12Background.tex
MI report - updated ch 2

In this project, the 9 software qualities mentioned above are the criteria ($m = 9$), while 29 software packages ($n = 29$) are compared for each of the $m$ criteria. The software are evaluated with the grading template in Appendix \ref{ap_grading_template} and a subjective score from one to ten is given for each quality for each package. For each quality, for a pair of packages $i$ and $j$, such that $score_i >= score_j$, the difference between two scores is $diff_{ij} = score_i - score_j$. The relationship between $A_{ij} = 1$ and $diff_{ij}$ is as follows:
\begin{itemize}
\item $A_{ij} = 1$ and $diff_{ij} = 0$ when criterion $i$ and criterion $j$ are equally important;
\item $A_{ij}$ increases when $diff_{ij}$ increases;
\item $A_{ij} = 9$ and $diff_{ij} = 9$ when criterion $i$ is extremely more important than criterion $j$.
\end{itemize}
Thus, we approximate the pairwise comparison result of $i$ versus $j$ by the following equation:
\begin{equation}
A_{ij} = min(score_i - score_j + 1, 9)
\end{equation}

>>>>

In this project, the 9 software qualities mentioned above are the criteria ($m = 9$), while 29 software packages ($n = 29$) are compared for each of the $m$ criteria. The software are evaluated with the grading template in Appendix \ref{ap_grading_template} and a subjective score from one to ten is given for each quality for each package. For each quality, for a pair of packages $i$ and $j$, such that $score_i >= score_j$, the difference between two scores is $\mathit{diff_{ij}} = score_i - score_j$. The relationship between $A_{ij} = 1$ and $\mathit{diff_{ij}}$ is as follows:
\begin{itemize}
\item $A_{ij} = 1$ and $\mathit{diff_{ij}} = 0$ when criterion $i$ and criterion $j$ are equally important;
\item $A_{ij}$ increases when $\mathit{diff_{ij}}$ increases;
\item $A_{ij} = 9$ and $\mathit{diff_{ij}} = 9$ when criterion $i$ is extremely more important than criterion $j$.
\end{itemize}
Thus, we approximate the pairwise comparison result of $i$ versus $j$ by the following equation:
\begin{equation}
A_{ij} = min(score_i - score_j + 1, 9)
\end{equation}
